Parity games in pushdown systems with parameters

### 2023-06-21 reachability/article.tex
up

\noindent
The games we are interested in are played by two players, called {\em player $0$} and {\em player $1$}. We will often write player $i$ to denote a general player for $i \in \{0,1 \}$,
and we will call player $1-i$ its {\em opponent}.

% Observe that there is no restriction on the number of the successors of a configuration in an arena. Also, we don’t require that (V, E) is a bipartite graph with corresponding partition {V 0 , V 1 }.

\iffalse
\noindent
In the case where $\Lambda$ is a singleton $\{ a\}$, we will abuse notation
and denote the arena by
$(S_0, S_1,{\rightarrow},\Omega)$, and we will see $(S,{\rightarrow})$
as an unlabeled transition system.
\fi

%  \subsubsection{Plays}

\noindent
A {\em play} in an arena $A=(S_0,S_1,\rightarrow)$ is a path in $(S,{\rightarrow})$ that is {\em maximal} in the following sense: it is either infinite or finite and if it is finite, then the target configuration is a dead end. 
A {\em partial play} in an arena $A=(S_0,S_1,\rightarrow)$ is a 
% sequence of configurations $s_{init} = s_0 s_1 \ldots \in S^\infty$ connected by the transition relation, i.e. such that $(v_i, v_{i+1}) \in T$.
prefix of a play in $A$.
Essentially plays can be seen as this: the two players, player $0$ and player $1$, move along the labeled transition system, taking turns either inﬁnitely often or until a dead end is reached.

@@

Once we have provided players with an arena, it remains to define  properly what the winning condition is in order to define a game. Given an arena $A = (S_0, S_1, \rightarrow)$, a {\em winning condition}
%$\win \subseteq S^\infty$
$\win$
is a subset  
of the set of maximal plays for $A$. A {\em game} is a pair $\mathcal{G}= (A, \win)$ which is composed of an arena $A$ and a winning condition $\win$.
Although a winning condition is in general an infinite object we are interested in winning conditions 
that can finitely be described.

A strategy $\sigma_0$ for player $0$ from position $s \in S$ is a {\em winning strategy
 from $s$} for player $0$ if 
% no matter which
% strategy $\sigma_{1}$ the other player pursues,
% the play $\pi(s, \sigma_0, \sigma_1)$ is in $\win$.
every maximal play starting from $s$ and consistent with $\sigma_0$ is in $\win$.
On the other hand, a strategy $\sigma_1$ for player $1$ from position $s \in S$ is a {\em winning strategy
 from $s$} for player $1$ if 
% no matter which
% strategy $\sigma_{0}$ the other player pursues,
% the play $\pi(s, \sigma_0, \sigma_1)$ is not in $\win$.
every maximal play starting from $s$ and consistent with $\sigma_1$ is not in $\win$.

@@

\begin{samepage}
\problemx{Reachability game}
{A reachability game $\mathcal{G}= ((S_0, S_1,{\rightarrow}),\win_F)$, an initial configuration $s \in S_0 \cup S_1$.}
{Does player $0$ have a winning strategy from $s$ in $\mathcal{G}$?}
\end{samepage}

% \subsection{Parity Games}

>>>>

\noindent
The games we are interested in are played by two players, called {\em player $0$} and {\em player $1$}. We will often write player $i$ to denote a general player for $i \in \{0,1 \}$,
and we will call player $1-i$ its {\em opponent}. 
A {\em play} in an arena $A=(S_0,S_1,\rightarrow)$ is a path in $(S,{\rightarrow})$ that is {\em maximal} in the following sense: it is either infinite or finite and if it is finite, then the target configuration is a dead end. 
A {\em partial play} in an arena $A=(S_0,S_1,\rightarrow)$ is a 
% sequence of configurations $s_{init} = s_0 s_1 \ldots \in S^\infty$ connected by the transition relation, i.e. such that $(v_i, v_{i+1}) \in T$.
prefix of a play in $A$.
Essentially plays can be seen as this: the two players, player $0$ and player $1$, move along the labeled transition system, taking turns either inﬁnitely often or until a dead end is reached.

@@

Once we have provided players with an arena, it remains to define  properly what the winning condition is in order to define a game. Given an arena $A = (S_0, S_1, \rightarrow)$, a {\em winning condition}
%$\win \subseteq S^\infty$
$\win$
is a subset  
of the set of maximal plays for $A$. A {\em game} is a pair $\mathcal{G}= (A, \win)$ which is composed of an arena $A$ and a winning condition $\win$.
Although a winning condition is in general an infinite object we are interested in winning conditions 
that can finitely be described.
A strategy $\sigma_0$ for player $0$ from position $s \in S$ is a {\em winning strategy
 from $s$} for player $0$ if 
% no matter which
% strategy $\sigma_{1}$ the other player pursues,
% the play $\pi(s, \sigma_0, \sigma_1)$ is in $\win$.
every maximal play starting from $s$ and consistent with $\sigma_0$ is in $\win$.
On the other hand, a strategy $\sigma_1$ for player $1$ from position $s \in S$ is a {\em winning strategy
 from $s$} for player $1$ if 
% no matter which
% strategy $\sigma_{0}$ the other player pursues,
% the play $\pi(s, \sigma_0, \sigma_1)$ is not in $\win$.
every maximal play starting from $s$ and consistent with $\sigma_1$ is not in $\win$.

@@

\problemx{Reachability game}
{A reachability game $\mathcal{G}= ((S_0, S_1,{\rightarrow}),\win_F)$, an initial configuration $s \in S_0 \cup S_1$.}
{Does player $0$ have a winning strategy from $s$ in $\mathcal{G}$? \\}
